Surrogate model of aligned-spin binary neutron star waveforms using Gaussian process regression

### 2018-01-15 paper/paper.tex
make paper compile

Next we choose a method to interpolate the residuals $\Delta\ln(A)(MF_j; \bx)$ and $\Delta\Phi(MF_j; \bx)$ at each of the frequency nodes $MF_j$ as a function of the five waveform parameters $\bx$. Most multivariate interpolation techniques (e.g. tensor spline or Chebyshev interpolation) require a function to be sampled on a rectangular grid, and thus suffer from the curse of dimensionality: the number of samples grows exponentially with the dimension $d$ ($N^d$ samples for $N$ points per dimension). For our 5-dimensional problem, $10^5$ waveform evaluations are needed for only 10 samples per parameter. At $\sim10$~minutes--1~day per EOB waveform on a standard CPU \MP{For which $f_\min$ are these times given?}, this is at the limit of what is reasonable. However, there are other methods that do not require a rectangular grid, and this allows us to choose more efficient experimental designs as discussed in Sec.~\ref{sec:design} below. The method we choose is Gaussian Process Regression (GPR)~\cite{RasmussenWilliams2006}.

>>>>

Next we choose a method to interpolate the residuals $\Delta\ln(A)(MF_j; \bx)$ and $\Delta\Phi(MF_j; \bx)$ at each of the frequency nodes $MF_j$ as a function of the five waveform parameters $\bx$. Most multivariate interpolation techniques (e.g. tensor spline or Chebyshev interpolation) require a function to be sampled on a rectangular grid, and thus suffer from the curse of dimensionality: the number of samples grows exponentially with the dimension $d$ ($N^d$ samples for $N$ points per dimension). For our 5-dimensional problem, $10^5$ waveform evaluations are needed for only 10 samples per parameter. At $\sim10$~minutes--1~day per EOB waveform on a standard CPU \MP{For which $f_\text{min}$ are these times given?}, this is at the limit of what is reasonable. However, there are other methods that do not require a rectangular grid, and this allows us to choose more efficient experimental designs as discussed in Sec.~\ref{sec:design} below. The method we choose is Gaussian Process Regression (GPR)~\cite{RasmussenWilliams2006}.
